Reproducible methods for modeling combined public transport and cycling trips and associated benefits: evidence from the biclaR tool

### 2024-09-02 paper/PaperCEUS/PaperCEUS_rev2_word.Rmd
test load files
knit again

stopsAML = sf::st_read("load/Stops_AML.geojson", quiet = TRUE)
stopsAML = stopsAML |> filter(mode != "Metropolitano") |>
  mutate(mode = factor(mode, levels = c("Comboio", "Ferry", "Metro Superficie", "Autocarro"),
                       labels = c("Train", "Ferry", "Tram", "Bus")))
routesAML = sf::st_read("load/Routes_AML.geojson", quiet = TRUE)
routesAML = routesAML |> 
  mutate(mode = factor(mode, levels = c("Comboio", "Ferry", "Metro Superficie", "Autocarro"),
                       labels = c("Train", "Ferry", "Tram", "Bus")))

>>>>

stopsAML = sf::st_read("load/StopsAML.geojson", quiet = TRUE)
stopsAML = stopsAML |> filter(mode != "Metropolitano") |>
  mutate(mode = factor(mode, levels = c("Comboio", "Ferry", "Metro Superficie", "Autocarro"),
                       labels = c("Train", "Ferry", "Tram", "Bus")))
routesAML = sf::st_read("load/RoutesAML.geojson", quiet = TRUE)
routesAML = routesAML |> 
  mutate(mode = factor(mode, levels = c("Comboio", "Ferry", "Metro Superficie", "Autocarro"),
                       labels = c("Train", "Ferry", "Tram", "Bus")))

### 2024-09-02 paper/PaperCEUS/PaperCEUS_rev2_word.tex
knit again

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
% TODO: Currently lineno needs to be loaded after amsmath because of conflict
% https://github.com/latex-lineno/lineno/issues/5
\usepackage{lineno} % add
  \linenumbers % turns line numbering on
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}

@@

\begin{figure}
\subfloat[Population distribution in the LMA\label{fig:lma-1}]{\includegraphics[width=0.5\linewidth,]{PaperCEUS_rev1_files/figure-latex/lma-1} }\subfloat[Trips/day in the LMA\label{fig:lma-2}]{\includegraphics[width=0.5\linewidth,]{PaperCEUS_rev1_files/figure-latex/lma-2} }\caption{\label{lma}Population and daily trips (origins) at each Municipality of the LMA, according to the 2021 census and the 2017 travel survey.}\label{fig:lma}
\end{figure}

@@

\begin{figure}
\subfloat[In percentage\label{fig:mododist-1}]{\includegraphics[width=0.5\linewidth,]{PaperCEUS_rev1_files/figure-latex/mododist-1} }\subfloat[In total\label{fig:mododist-2}]{\includegraphics[width=0.5\linewidth,]{PaperCEUS_rev1_files/figure-latex/mododist-2} }\caption{\label{mododist}Trips in the LMA by inter/intra municipal and mode, according to the travel survey.}\label{fig:mododist}
\end{figure}

@@

{\centering \includegraphics[width=0.6\linewidth,]{PaperCEUS_rev1_files/figure-latex/map1-1}

@@

\begin{figure}
\subfloat[Potential new Bicycle + PT trips\label{fig:mapzones-1}]{\includegraphics[width=0.5\linewidth,]{PaperCEUS_rev1_files/figure-latex/mapzones-1} }\subfloat[Proportion of total potential modal shift in the LMA\label{fig:mapzones-2}]{\includegraphics[width=0.5\linewidth,]{PaperCEUS_rev1_files/figure-latex/mapzones-2} }\caption{\label{mapzones}Potential Bicycle + PT daily trips for the 10\% target and direct routing, by municipality (origins). The percentages are shown for municipalities with values above 4\%.}\label{fig:mapzones}
\end{figure}

>>>>

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
% TODO: Currently lineno needs to be loaded after amsmath because of conflict
% https://github.com/latex-lineno/lineno/issues/5
\usepackage{lineno} % add
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}

@@

\begin{figure}
\subfloat[Population distribution in the LMA\label{fig:lma-1}]{\includegraphics[width=0.5\linewidth,]{PaperCEUS_rev2_word_files/figure-latex/lma-1} }\subfloat[Trips/day in the LMA\label{fig:lma-2}]{\includegraphics[width=0.5\linewidth,]{PaperCEUS_rev2_word_files/figure-latex/lma-2} }\caption{\label{lma}Population and daily trips (origins) at each Municipality of the LMA, according to the 2021 census and the 2017 travel survey.}\label{fig:lma}
\end{figure}

@@

\begin{figure}
\subfloat[In percentage\label{fig:mododist-1}]{\includegraphics[width=0.5\linewidth,]{PaperCEUS_rev2_word_files/figure-latex/mododist-1} }\subfloat[In total\label{fig:mododist-2}]{\includegraphics[width=0.5\linewidth,]{PaperCEUS_rev2_word_files/figure-latex/mododist-2} }\caption{\label{mododist}Trips in the LMA by inter/intra municipal and mode, according to the travel survey.}\label{fig:mododist}
\end{figure}

@@

{\centering \includegraphics[width=0.6\linewidth,]{PaperCEUS_rev2_word_files/figure-latex/map1-1}

@@

\begin{figure}
\subfloat[Potential new Bicycle + PT trips\label{fig:mapzones-1}]{\includegraphics[width=0.5\linewidth,]{PaperCEUS_rev2_word_files/figure-latex/mapzones-1} }\subfloat[Proportion of total potential modal shift in the LMA\label{fig:mapzones-2}]{\includegraphics[width=0.5\linewidth,]{PaperCEUS_rev2_word_files/figure-latex/mapzones-2} }\caption{\label{mapzones}Potential Bicycle + PT daily trips for the 10\% target and direct routing, by municipality (origins). The percentages are shown for municipalities with values above 4\%.}\label{fig:mapzones}
\end{figure}
